### 2017-06-30 motivation.tex
Figures.

\begin{figure}
\centering
\begin{ocaml}
let new_order_ d_id c_id item_reqs = atomically do
  dist <- SQL.select1 District (fun d -> d.d_id = d_id);
  let o_id = dist.d_next_o_id;
  SQL.update District (fun d -> {d with d_next_o_id =d_next_o_id + 1})
                      (fun d -> d.d_id = d_id );
  SQL.insert Order {o_id=o_id;  o_d_id=d_id; 
                    o_c_id=c_id; o_ol_cnt=S.size item_reqs; };
  foreach item_reqs @@ fun item_req -> do
    stk <- SQL.select1 Stock (fun s -> s.s_i_id = item_req.ol_i_id);
    let s_qty' = if stk.s_qty >= item_req.ol_qty + 10 
                then stk.s_qty - item_req.ol_qty 
                else stk.s_qty - item_req.ol_qty + 91;
    SQL.update Stock (fun s -> {s with s_qty = s_qty'}) 
                     (fun s -> s.s_i_id = item_req.ol_i_id);
    SQL.insert Order_line {ol_o_id=o_id; ol_d_id=d_id; 
                           ol_i_id=item_req.ol_i_id; ol_qty=item_req.ol_qty}

\end{ocaml}
\caption{\small Concurrent withdraw transactions}
\label{fig:new_order_code}
\vspace*{-10pt}
\end{figure}

@@

@@

\begin{figure}[!h]
\centering
\subcaptionbox {
  {\sc rc} Execution 1
  \label{fig:motiv-eg-1-a}
} [
  0.55\columnwidth
] {
  \includegraphics[scale=0.6]{Figures/motiv-eg-1-a}
}
%\hspace*{0.5in}
\subcaptionbox {
  {\sc rc} Execution 2
  \label{fig:motiv-eg-1-b}
}{
  \includegraphics[scale=0.6]{Figures/motiv-eg-1-b}
}
\caption{\small A possible execution of the program shown in Fig.~\ref{fig:motiv-eg-1} under
  \iso{Read Committed} isolation level. Transaction \C{Wd1} is shown
  against lighter green background, and transaction \C{Wd2} against
  darker red background. Each transaction reads the balance (\C{B})
  twice, hence two \C{Reads}.}
\label{fig:rc-ex}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{ocaml}
let new_order d_id c_id item_reqs = atomically do
  dist <- SQL.select1 District (fun d -> d.d_id = d_id);
  let o_id = dist.d_next_o_id;
  SQL.update District (fun d -> {d with d_next_o_id =d_next_o_id + 1})
                      (fun d -> d.d_id = d_id );
  SQL.insert Order {o_id=o_id;  o_d_id=d_id; 
                    o_c_id=c_id; o_ol_cnt=S.size item_reqs; };
  foreach item_reqs @@ fun item_req -> do
    stk <- SQL.select1 Stock (fun s -> s.s_i_id = item_req.ol_i_id &&
                                       s.s_d_id = d_id);
    let s_qty' = if stk.s_qty >= item_req.ol_qty + 10 
                then stk.s_qty - item_req.ol_qty 
                else stk.s_qty - item_req.ol_qty + 91;
    SQL.update Stock (fun s -> {s with s_qty = s_qty'}) 
                     (fun s -> s.s_i_id = item_req.ol_i_id);
    SQL.insert Order_line {ol_o_id=o_id; ol_d_id=d_id; 
                           ol_i_id=item_req.ol_i_id; ol_qty=item_req.ol_qty}

\end{ocaml}
\caption{TPC-C \C{new\_order} transaction}
\label{fig:new_order_code}
\vspace*{-10pt}
\end{figure}

@@

\begin{figure}[!t]
\includegraphics[scale=0.5]{Figures/schema}
\caption{Database schema of TPC-C's order management system.
  Columns against highlighted background are primary keys. Arrows denote
  foreign key relationships.}
\label{fig:schema}
\end{figure}

@@

\begin{figure}[!h]
\centering
\subcaptionbox {
  {\sc rc} Execution 1
  \label{fig:motiv-eg-1-b}
} [
  0.55\columnwidth
] {
  \includegraphics[scale=0.45]{Figures/motiv-eg-1-b}
}
%\hspace*{0.5in}
\subcaptionbox {
  {\sc rc} Execution 2
  \label{fig:motiv-eg-1-a}
}{
  \includegraphics[scale=0.45]{Figures/motiv-eg-1-a}
}
  \caption{\small RC executions involving two instances ($T_1$ and
  $T_2$) of the \C{new\_order} transaction of
  Fig.~\ref{fig:new_order_code}. 
  Each instance reads the \C{d\_id} \C{District} record twice, second
  time to (atomically) update the \C{d\_next\_o\_id} field.}
\label{fig:rc-ex}
\end{figure}
